---
title: "Ghana Health Facilities"
author: "Reginald"
date: "August 19, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries to be used

```{r, message=FALSE}
library(tidyverse)
library(rgdal)

```

```{r, include = FALSE}

hlth <- read.csv("C:/Users/Senyo/Downloads/HEALTH FACILITIES IN GHANA.csv")

gh_shp <- readOGR(dsn = "C:/Users/Senyo/Downloads/GHA_adm", layer = "GHA_adm1")

```


##Skimming through the dataset
```{r }
str(hlth)
```

Checking for missing values in each column
```{r}
hlth %>% 
  purrr::map_df(~sum(is.na(.)))
```
24 missing coordinates of the health facilities

### Checking the levels of ownership
```{r}
levels(hlth$Ownership) 
```
Need to streamline some of the levels

```{r}
hlth <- hlth %>% 
  mutate_at(.vars = vars(Ownership), .funs = forcats::fct_recode, Private = "private", Islamic = "Muslim", 
            Government = "government", Government = "Clinic", Islamic = "Mission") %>% 
  mutate_at(.vars = vars(Type), .funs = fct_recode, "Health Centre" = "Centre", CHPS ="CPHS", Clinic = "clinic",
            "District Health Directorate"= "DHD", "Reproductive and Child Health" = "RCH",
            "Municipal Health Directorate" = "Municipal  Health Directorate")
```


###Collapsing the health facilities into 4 categories
```{r}
hlth %>% 
  mutate_at(.vars = vars(Type), .funs = funs(nType = forcats::fct_collapse), 
            "health provider" = c("Health Centre", "CHPS",  "Clinic", "Hospital", "District Hospital", 
                                  "Metropolitan Hospital", "Municipal Hospital", "Regional Hospital", 
                                  "Teaching Hospital", "Maternity Home", "Reproductive and Child Health",
                                  "Psychiatric Hospital", "Polyclinic"),
            "directorate" = c("District Health Directorate", "Metropolitan Health Directorate", 
                              "Municipal Health Directorate", "Regional Health Directorate"),
            "training and research" = c("Training Institution", "Research Institution")) %>% 
  group_by(nType) %>% 
  summarise(n = n())
```


```{r, warning=FALSE}
gh <- broom::tidy(gh_shp)
gh$id <- as.character(gh$id)
```


```{r}
ggplot()+
  geom_polygon(data = gh, aes(x = long, y = lat, group = group), colour = "grey") +
  geom_point(data = hlth, aes(x = Longitude, y = Latitude, colour = Ownership)) +
  coord_fixed(ratio = 1) +
  theme_bw() +
  theme(axis.text = element_blank(), # change the theme options 
        axis.title = element_blank(), # remove axis titles 
        axis.ticks = element_blank()) 
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
